Active Learning with Sentence Error Classification in Machine Translation

### 2020-10-10 Paper/active-learning.tex
update related work

Active Learning has been widely studied in Natural Language Processing and often integrated as an effective approach in low resource scenaria in modern neural network systems and for a variety of tasks. 
\citet{lu2020investigating} suggest that representations generated from pre-trained transformer neural network models, are more effective in Active Learning for text classification, than using simpler word embeddings.

Closer to our Machine Translation objective, \citet{zhang2018active} propose two methods, for sentence selection based on considering semantic similarity between sentence embeddings or decoder probabilities as tokens of translation quality, while \citet{peris2020active} explore the application of active learning techniques in the interactive translation of large data streams. The latter work uses the attention mechanism of a neural machine translation system to query only for those sentences worthy of human annotation for translation.

In a more recent approach, \citet{zeng2019empirical} perform an empirical evaluation of different AL methods for Transformers \cite{vaswani2017attention}, analyzing data-driven approaches, that sample instances using two sets of labeled and unlabeled sentences, and model-driven methods, which additionally incorporate information from the current model into sampling. However their work notes the weak performance of Coverage Sampling compared to the other techniques, due to the complex nature of the state-of-the art multi-layer multi-head Natural Language Processing architectures, a phenomenon we are addressing with the current work.

A line of work has also explored the shortcomings of Active Learning approaches in Machine Translation. \citet{lowell2018practical} observe the performance drop issues arising across different models and tasks and discuss the methods' generalization constraints. Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a neural machine translation system in learning sentence semantic representations.

>>>>

Active Learning (AL) has been widely studied in Natural Language Processing and integrated in modern systems as an effective approach in low resource scenaria for a variety of tasks. 
\citet{lu2020investigating} investigate AL in text classification, suggesting the effectiveness of representations generated from pre-trained Transformer models, compared to simple word embeddings.

In NMT, \citet{zhang2018active} propose two methods for sentence selection, considering either the semantic similarity between sentence embeddings or the decoder probabilities as tokens of translation quality, while \citet{peris2020active} explore AL in the interactive translation of large data streams. The latter work uses an NMT attention mechanism to query only for those sentences worthy of human annotation for translation.

\citet{zeng2019empirical} perform an empirical evaluation of AL methods for Transformers, analyzing data- and model-driven sentences' sampling techniques. Their work notes the weak performance of Coverage Sampling, due to the complex nature of multi-layer multi-head architectures, an issue we are addressing with the current work.

A line of work has also explored the shortcomings of AL approaches in NMT. \citet{lowell2018practical} observe performance drop issues arising across different models and tasks and discuss the methods' generalization constraints. Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a NMT system in learning sentence semantic representations.

### 2020-10-10 Paper/error-classification.tex
update related work

There exists a significant body of work in the area of error classification of text for machine translation, and proposed methods can be primarily divided into manual or automatic. In the former category, approaches focus on describing detailed error typologies to be used in conducting a systematic manual error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}. On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output sentence of a Machine Translation system and its reference translation. Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous works to multi-label and multi-error automatic classification \citet{popovic2019automatic}.

In most recent approaches, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}. The state of the art methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of prior methods that require large amounts of labeled data to perform efficiently.

>>>>

There exists a significant body of work in the area of text error classification in MT, and proposed methods are primarily divided into manual or automatic. In the former category, approaches describe detailed error typologies to be used in conducting a systematic error annotation \cite{fishel2011automatic,vilar2006error, lommel2014multidimensional, farrus2010linguistic, costa2015linguistically}. On the other hand,  automatic error classification tools \cite{zeman2011addicter, popovic2011hjerson,popovic2015poor} detect predefined error types, by measuring the alignment of the output sentence of a MT system and its reference translation. Further work in this direction incorporates the idea that a certain sentence error can fit in more than one categories \cite{klubivcka2018quantitative, lommel2014assessing} and extends previous works to multi-label and multi-error automatic classification \citep{popovic2019automatic}.

Most recently, error detection and classification are examined as applications of neural sequence labeling methods, which aim to detect errors and predict their surrounding context \cite{rei2017semi}. The latest methods utilize powerful contextual word embeddings in an unsupervised setting \cite{bell2019context}, and overcome the disadvantages of older ones requiring large amounts of labeled data to perform efficiently.

### 2020-10-10 Paper/linguistic-representations.tex
update related work

The work of \citet{belinkov2020linguistic} is a significant step in collecting and interpreting all approaches that examine the linguistic nature of the representations learned by modern complex neural network Machine Translation models, specifically LSTMs \citep{bahdanau2014neural}. The authors focus on three large categories of language properties, morphology, syntax and semantics, show that each category of information is better captured at a different layer of the architecture, and set the ground for further exploration of linguistic representations of more state-of-the-art models, such as the Transformer \citep{vaswani2017attention}.

>>>>

The work of \citet{belinkov2020linguistic} is a significant step in presenting all approaches that examine the linguistic nature of the representations learned for MT in modern complex neural networks, specifically in LSTMs \citep{bahdanau2014neural}. The authors focus on three large categories of language properties, morphology, syntax and semantics, show that each type of information is better captured at a different layer of the architecture, and set the ground for further exploration of linguistic representations in MT with Transformer-based models \citep{vaswani2017attention}.
